Fitting metabolic models to dissolved oxygen data: The Estuarine BAyesian Single-station Estimation method

### 2023-08-25 manu-draft.qmd
reproc figs and tables for #4 but still jacked up

![The default prior distributions for $a$, $R$, and $b$ used in EBASE. All priors are normal distributions and truncated to positive values. $b$ is also truncated to a maximum of 0.502.](figs/priorplot.png){#fig-priorplot fig-align="center"}

@@

![Synthetic time series for one year of continuous data at Apalachicola Bay. Synthetic input to EBASE was the (a) dissolved oxygen time series, with results compared to the (b) synthetic $a$ parameter and (c) synthetic metabolic estimates for gross primary production ($P$), the negative of ecosystem respiration ($-R$), and gas exchange ($D$).](figs/synapa.png){#fig-synapa}

@@

![Comparison of EBASE results to a synthetic time series created with known metabolic parameters. Results are compared for unique combinations of prior distributions and optimization period. The means ($\mu$) and standard deviations ($\sigma$) are evaluated as low (L) or high (H) values (see text for details) and the optimization period for EBASE is one day, seven days, or thirty days. The metabolic results for dissolved oxygen (DO), gross primary production (P), ecosystem respiration (R), gas exchange (D), and the $a$ parameter are evaluated based on Nash-Sutcliffe Efficiency (NSE) values between the EBASE results and synthetic values. NSE values from zero to one (green) indicate EBASE has recovered the synthetic parameters with values closer to 1 being a better approximation, whereas negative values indicate poor recovery. The color scale for NSE is also exponentially transformed to minimize the influence of large negative values on the visual display. The $b$ parameter is a fixed constant and was not evaluated. Rankings of each combination as the median NSE value across all parameters in a row are shown on the right, with the top three as black/bold and bottom three as black/italic.](figs/priorcomp.png){#fig-priorcomp}

>>>>

![The default prior distributions for $a$, $R$, and $b$ used in EBASE. All priors are normal distributions and truncated to positive values. $b$ is also truncated to a maximum of 0.502 $\left(\text{cm}/\text{hr}\right)/\left(\text{m}^2/\text{s}^2\right)$.](figs/priorplot.png){#fig-priorplot fig-align="center"}

@@

![Synthetic time series for one year of continuous data at Apalachicola Bay. Synthetic input to EBASE was the (a) dissolved oxygen time series, with results compared to the (b) synthetic $a$ parameter and (c) synthetic metabolic estimates for gross primary production ($P$), the negative of ecosystem respiration ($-R$), and gas exchange ($-D$).](figs/synapa.png){#fig-synapa}

@@

![Comparison of EBASE results to a synthetic time series created with known model parameters. ($a$, $R$, and $b$). Results are compared for unique combinations of prior distributions and optimization period. The means ($\mu$) and standard deviations ($\sigma$) are evaluated as low (L) or high (H) values (see text for details) and the optimization period for EBASE is one day, seven days, or thirty days. The model predictions of dissolved oxygen (DO), gross primary production (P), ecosystem respiration (R), gas exchange (D), and the $a$ parameter are evaluated based on Nash-Sutcliffe Efficiency (NSE) values between the EBASE results and synthetic values. NSE values from zero to one (green) indicate EBASE has some skill in recovering the synthetic values of DO, $D$, $P$, $R$ , and $a$, with values closer to 1 being a better approximation, whereas negative values indicate no skill. The color scale for NSE is also exponentially transformed to minimize the influence of large negative values on the visual display. The $b$ parameter is a fixed constant and was not evaluated. Rankings of each combination as the median NSE value across all five model outputs in a row are shown on the right, with the top three as black/bold and bottom three as black/italic.](figs/priorcomp.png){#fig-priorcomp}
